---
title: "Wendys Exp"
---

What devices are these tweets coming from? We can use the "sourcestatus" column to see the original device used to make each tweet. 

```{r}
wendys_DF <- read.table(file = "./RawData/WendysTweets.txt", 
                    header = FALSE, fill = TRUE)

sort(table(wendys_DF$V12), decreasing = TRUE)

iphone <- length(grep("iphone",wendys_DF$V12, ignore.case = TRUE))
android <- length(grep("android",wendys_DF$V12, ignore.case = TRUE))
webtwit <- length(grep("twitter web",wendys_DF$V12, ignore.case = TRUE))
ipad <- length(grep("ipad",wendys_DF$V12, ignore.case = TRUE))
```

Only 3 sources take up the vast majority of tweet origination, with iPhone possessing the most tweets by a landslide. Android is in a distant second. Mobile devices clearly originate the vast majority of tweets, with the Twitter Web Client in a far 3rd. The iPad is the only other source with more than 10 devices out of 1000 original tweets.

```{r}
barplot(c(iphone,
       android,
       webtwit,
       ipad,
       length(wendys_DF$V12) - 1 - iphone - android - webtwit - ipad), 
       names.arg =  c("iPhone",
                      "Android",
                      "Web Client",
                      "iPad",
                      "Other"),
       col = c('#69D2E7', '#A7DBD8', '#E0E4CC', '#F38630', '#FA6900'),
       xlab = "Tweet Original Source", ylab = "Frequency", 
       main = "Frequencies of Different Tweet Sources")

pdf(file = "./Plots/WendysSourcePlot.pdf")
#run above plot
dev.off()

png(file = "./Plots/WendysSourcePlot.png")
#run above plot
dev.off()
```
